EnVision CF Analyses

### 2025-10-07 Christine Chan/EnVision CF/envision_analyses.qmd
enVision updates on pre/post ETI, repeated measures ROC, and EDA

```{r}
# Limit to those with CGM data (based on mean glucose) and OGTT diagnosis
# Remove CC0083 per Christine (weird CGM)
df <- final_df %>%
    filter(!is.na(mean_sensor), !is.na(Diagnosis), study_id != "CC0083")
# Change specific diagnoses per Christine
df$Diagnosis[df$study_id == "WU0019"] <- c("NGT", "NGT")
df$Diagnosis[df$study_id == "IA0080"] <- "IGT"
# Convert CV units to match Scully et al.
df$cv <- df$cv * 100
# First CGM and OGTT pair only
# df <- df %>%
#     group_by(study_id) %>%
#     slice_min(Date)
```

@@

```{r}
#| message: false
#| warning: false
#| fig-height: 12
#| fig-width: 16
# Dotplot
box_p1 <- ggplot(
    df,
    aes(
        x = Dysglycemia,
        y = percent_time_over_140,
        colour = Dysglycemia,
        text = study_id
    )
) +
    geom_jitter() +
    geom_hline(yintercept = 17.5, color = "red") +
    geom_hline(yintercept = 11.3, color = "purple") +
    ggtitle("% Time Over 140 (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p2 <- ggplot(
    df,
    aes(x = Dysglycemia, y = percent_time_over_180, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 3.4, color = "red") +
    geom_hline(yintercept = 3.1, color = "purple") +
    ggtitle("% Time Over 180 (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p3 <- ggplot(
    df,
    aes(x = Dysglycemia, y = mean_sensor, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 112, color = "red") +
    geom_hline(yintercept = 101, color = "purple") +
    ggtitle("Mean glucose (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p4 <- ggplot(
    df,
    aes(x = Dysglycemia, y = cv, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 30.6, color = "red") +
    geom_hline(yintercept = 27.7, color = "purple") +
    ggtitle("Coefficient of Variation (%)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p5 <- ggplot(
    df,
    aes(x = Dysglycemia, y = a1c_result, colour = Dysglycemia)
) +
    geom_jitter() +
    geom_hline(yintercept = 5.8, color = "red") +
    geom_hline(yintercept = 5.75, color = "purple") +
    ggtitle("HbA1c (%)") +
    theme_bw(base_size = 12) +
    theme(
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p <- box_p1 + box_p2 + box_p4 + box_p3 + box_p5 + plot_layout(ncol = 5)
box_p
ggplotly(box_p1, tooltip = c("text"))
ggplotly(box_p2, tooltip = c("text"))
ggplotly(box_p4, tooltip = c("text"))
ggplotly(box_p3, tooltip = c("text"))
ggplotly(box_p5, tooltip = c("text"))
```

>>>>

```{r}
# Limit to those with CGM data (based on mean glucose) and OGTT diagnosis
# Remove CC0083 per Christine (weird CGM)
df <- final_df %>%
    filter(!is.na(mean_sensor), !is.na(Diagnosis), study_id != "CC0083")
# Change specific diagnoses per Christine
df$Diagnosis[df$study_id == "WU0019"] <- c("NGT", "NGT")
df$Diagnosis[df$study_id == "IA0080"] <- "IGT"
df$Dysglycemia[df$study_id == "WU0019"] <- c("NGT", "NGT")
df$Dysglycemia[df$study_id == "IA0080"] <- "AGT"
df$CFRD[df$study_id == "WU0019"] <- c("CFRD-", "CFRD-")
df$CFRD[df$study_id == "IA0080"] <- "CFRD-"
# Convert CV units to match Scully et al.
df$cv <- df$cv * 100
# First CGM and OGTT pair only
# df <- df %>%
#     group_by(study_id) %>%
#     slice_min(Date)
```

@@

```{r}
#| message: false
#| warning: false
#| fig-height: 12
#| fig-width: 16
# Dotplot
box_p1 <- ggplot(
    df,
    aes(
        x = Dysglycemia,
        y = percent_time_over_140,
        colour = Dysglycemia,
        text = study_id
    )
) +
    geom_jitter() +
    geom_hline(yintercept = 17.5, color = "red") +
    geom_hline(yintercept = 11.3, color = "purple") +
    ggtitle("% Time Over 140 (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p2 <- ggplot(
    df,
    aes(
        x = Dysglycemia,
        y = percent_time_over_180,
        colour = Dysglycemia,
        text = study_id
    )
) +
    geom_jitter() +
    geom_hline(yintercept = 3.4, color = "red") +
    geom_hline(yintercept = 3.1, color = "purple") +
    ggtitle("% Time Over 180 (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p3 <- ggplot(
    df,
    aes(x = Dysglycemia, y = mean_sensor, colour = Dysglycemia, text = study_id)
) +
    geom_jitter() +
    geom_hline(yintercept = 112, color = "red") +
    geom_hline(yintercept = 101, color = "purple") +
    ggtitle("Mean glucose (mg/dL)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p4 <- ggplot(
    df,
    aes(x = Dysglycemia, y = cv, colour = Dysglycemia, text = study_id)
) +
    geom_jitter() +
    geom_hline(yintercept = 30.6, color = "red") +
    geom_hline(yintercept = 27.7, color = "purple") +
    ggtitle("Coefficient of Variation (%)") +
    theme_bw(base_size = 12) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p5 <- ggplot(
    df,
    aes(x = Dysglycemia, y = a1c_result, colour = Dysglycemia, text = study_id)
) +
    geom_jitter() +
    geom_hline(yintercept = 5.8, color = "red") +
    geom_hline(yintercept = 5.75, color = "purple") +
    ggtitle("HbA1c (%)") +
    theme_bw(base_size = 12) +
    theme(
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
    ) +
    scale_color_manual(values = c("#4DA8DA", "#80D8C3", "#FFD66B"))
box_p <- box_p1 + box_p2 + box_p4 + box_p3 + box_p5 + plot_layout(ncol = 5)
box_p
ggplotly(box_p1, tooltip = c("text"))
ggplotly(box_p2, tooltip = c("text"))
ggplotly(box_p3, tooltip = c("text"))
ggplotly(box_p4, tooltip = c("text"))
ggplotly(box_p5, tooltip = c("text"))
```
